---
title: "ms final project"
author: "RanChen"
date: "2024-11-19"
output:
  pdf_document: default
  html_document: default
---


Data input
```{r}
library(haven)
library(e1071)
library(survey)
library(ggplot2)
library(tidyr)
library(dplyr)
library(randomForest)
library(pROC)
library(xgboost)
library(caret)





data1<-read_xpt("GLU_L.XPT")
data2<-read_xpt("DEMO_L.XPT")
data3<-read_xpt("SMQ_L.XPT")
data4<-read_xpt("GHB_L.XPT")#HBA1C
data5<-read_xpt("PAQ_L.XPT")
data6<-read_xpt("DIQ_L.XPT")
data7<-read_xpt("ALQ_L.XPT")
data8<-read_xpt("INQ_L.XPT")
data9<-read_xpt("SLQ_L.XPT")
data10<-read_xpt("BMX_L.XPT")
 

data_list<-list(data1, data2, data3, data4, data5, data6,data7,data8,data9,data10)

merged_data<-Reduce(function(x, y) merge(x, y, by = "SEQN"), data_list)

#colnames(merged_data)

#delete the columns we don't need
merged_data<-merged_data %>% select(-"DMDYRUSR", - "DMQMILIZ", -"RIDAGEMN",  -"RIDEXAGM", -"RIDEXMON", -"RIDSTATR", -"SDDSRVYR", -"SEQN", -"DIQ160", -"DIQ180", -"DIQ050", -"DID060", -"DIQ060U", -"DIQ070", -"LBXGLU", -"SMD630", -"SMD641", -"SMD650", -"SMQ020",  -"ALQ130", -"ALQ142", -"ALQ151", -"ALQ170", -"ALQ270", -"ALQ280", -"INDFMMPC", -"INDFMMPI", -"SLQ310", -"SLQ330", -"BMDBMIC", -"BMDSTATS", -"BMIARMC", -"BMIARML", -"BMIHEAD", -"BMIHIP", -"BMIHT", -"BMILEG", -"BMIRECUM", -"BMIWAIST", -"BMIWT", -"DID040", -"DMDHREDZ",-"DMDHRGND", -"DMDHRMAZ",-"DMDHSEDZ")

#nrow(merged_data)
#head(merged_data)
```


Data Cleaning
```{r}

cleaned_data <- merged_data %>%
  filter(!is.na(WTMEC2YR)) %>%
  filter(RIDAGEYR >= 20) %>%
  filter(RIDEXPRG != 1 | is.na(RIDEXPRG))



cleaned_data <- cleaned_data %>%
    mutate(
      diabetes = ifelse(DIQ010 == 1 | LBDGLUSI >= 7, 1, 0),
      prediabetes = ifelse((LBDGLUSI >= 5.6 & LBDGLUSI < 7), 1, 0),
      nondiabetes = ifelse(LBDGLUSI < 5.6 & DIQ010 != 1, 1, 0)
    )

cleaned_data <- cleaned_data %>%
    mutate(
      diabetes = replace_na(diabetes, 0),
      prediabetes = replace_na(prediabetes, 0),
      nondiabetes = replace_na(nondiabetes, 0)
    )
data<-cleaned_data %>% select(-"DIQ010",-"LBDGLUSI")


#age
diff_rows <- data[!is.na(data$DMDHRAGZ) & !is.na(data$RIDAGEYR) & data$DMDHRAGZ != data$RIDAGEYR, ]
#print(head(diff_rows[, c("DMDHRAGZ", "RIDAGEYR")]))
#nrow(diff_rows)
data$age<-coalesce(data$RIDAGEYR, data$DMDHRAGZ)
data<- data%>%select(-"DMDHRAGZ", -"RIDAGEYR")


#sum(data$nondiabetes)

#colnames(data)
```



design
```{r}
library(survey)


interview_data<-data %>% select( "RIAGENDR","RIDRETH1","RIDRETH3","DMDBORN4","DMDEDUC2","DMDMARTZ", 
                                 "DMDHHSIZ","WTINT2YR","WTMEC2YR","SDMVSTRA",
                                 "SDMVPSU","SMQ040","PAD790Q","PAD790U","PAD800",
                                 "PAD810Q","PAD810U","PAD820","PAD680","ALQ111","ALQ121", "IND310","SLD012",
                                 "SLD013" , "diabetes","prediabetes" ,"nondiabetes","age")
exam_data<- data %>% select("WTSAF2YR","RIDRETH1", "RIDRETH3", "DMDBORN4", "DMDEDUC2", "DMDMARTZ", 
                             "DMDHHSIZ", "WTMEC2YR", "SDMVSTRA",
                            "SDMVPSU", "INDFMPIR", "WTPH2YR", "LBXGH", "BMXWT", "BMXRECUM", "BMXHEAD", "BMXHT", "BMXBMI",
                            "BMXLEG", "BMXARML", "BMXARMC", "BMXWAIST", "BMXHIP", "diabetes", "prediabetes", "nondiabetes","age")



interview_design <- svydesign(
  id = ~SDMVPSU,
  strata = ~SDMVSTRA,
  weights = ~WTINT2YR,
  data = interview_data,
  nest = TRUE
)

exam_design <- svydesign(
  id = ~SDMVPSU,
  strata = ~SDMVSTRA,
  weights = ~WTMEC2YR,
  data = exam_data,
  nest = TRUE
)
```


EDA
```{r}
#diabetes barplot
diabetes_status <- svytable(~diabetes, interview_design)
prediabetes_status <- svytable(~prediabetes, interview_design)
nondiabetes_status <- svytable(~nondiabetes, interview_design)

status_df <- data.frame(
  Status = c("Diabetes", "Prediabetes", "Non-diabetes"),
  Count = c(diabetes_status[2], prediabetes_status[2], nondiabetes_status[2])
)

status_df$Percentage <- status_df$Count / sum(status_df$Count) * 100

ggplot(status_df, aes(x = Status, y = Count, fill = Status)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), 
            position = position_dodge(width = 0.9), 
            vjust = 0) +
  scale_fill_manual(values = c("#FF9999", "#66B2FF", "#99FF99")) +
  labs(title = "Distribution of Diabetes Status (Weighted)") +
  theme_minimal()



#violin plot
#age vs status
age_data <- data.frame(
  Age = interview_data$age,
  Weight = interview_data$WTINT2YR,
  Status = case_when(
    interview_data$diabetes == 1 ~ "Diabetes",
    interview_data$prediabetes == 1 ~ "Prediabetes",
    TRUE ~ "Non-diabetes"
  )
)

ggplot(age_data, aes(x = Status, y = Age, fill = Status, weight = Weight)) +
  geom_violin(trim = FALSE) +
  geom_boxplot(width = 0.1, alpha = 0.2) +
  scale_fill_manual(values = c("#FF9999", "#66B2FF", "#99FF99")) +
  labs(title = "Age Distribution by Diabetes Status (Weighted)",
       y = "Age") +
  theme_minimal()

#gender vs status
diabetes_by_gender <- svytable(~RIAGENDR + diabetes, interview_design)
prediabetes_by_gender <- svytable(~RIAGENDR + prediabetes, interview_design)
nondiabetes_by_gender <- svytable(~RIAGENDR + nondiabetes, interview_design)

gender_status_df <- data.frame(
  Gender = rep(c("Male", "Female"), 3),
  Status = rep(c("Diabetes", "Prediabetes", "Non-diabetes"), each = 2),
  Count = c(
    diabetes_by_gender[1,2], diabetes_by_gender[2,2],
    prediabetes_by_gender[1,2], prediabetes_by_gender[2,2],
    nondiabetes_by_gender[1,2], nondiabetes_by_gender[2,2]
  )
)

gender_status_df <- gender_status_df %>%
  group_by(Gender) %>%
  mutate(Percentage = Count / sum(Count) * 100)

ggplot(gender_status_df, aes(x = Gender, y = Percentage, fill = Status)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#FF9999", "#66B2FF", "#99FF99")) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5)) +
  labs(title = "Distribution of Diabetes Status by Gender (Weighted)",
       x = "Gender",
       y = "Percentage") +
  theme_minimal()




#bmi distribution
bmi_data <- data.frame(
  BMI = exam_data$BMXBMI,
  Weight = exam_data$WTMEC2YR,
  Status = case_when(
    exam_data$diabetes == 1 ~ "Diabetes",
    exam_data$prediabetes == 1 ~ "Prediabetes",
    TRUE ~ "Non-diabetes"
  )
)

ggplot(bmi_data, aes(x = BMI, fill = Status, weight = Weight)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("#FF9999", "#66B2FF", "#99FF99")) +
  labs(title = "BMI Distribution by Diabetes Status (Weighted)",
       x = "BMI",
       y = "Density") +
  theme_minimal()
```



Variable Selection
Interview Data
```{r}
#nrow(interview_data)

#unique(data$SMQ040)
interview_data <- interview_data %>%
  mutate(
    smoking = case_when(
      SMQ040 %in% c(1, 2) ~ 1,
      SMQ040 == 3 | is.na(SMQ040) ~ 0
    )
  )


interview_data <- interview_data %>%
  mutate(
    vigorous_time = case_when(
      PAD810U == 2 ~ PAD810Q * 60 * PAD820,
      PAD810U == 1 ~ PAD810Q * PAD820,
      TRUE ~ NA_real_
    )
  )

interview_data <- interview_data %>%
  mutate(
    moderate_time = case_when(
      PAD790U == "D" ~ PAD790Q *PAD800,
      PAD790U == "W" ~ PAD790Q *PAD800 /7,
      PAD790U == "M" ~ PAD790Q *PAD800 /30,
      PAD790U == "Y" ~ PAD790Q *PAD800 /360,
      TRUE ~ 0
    )
  )
interview_data <- interview_data %>%
  mutate(
    vigorous_time = case_when(
      PAD810U == "D" ~ PAD810Q *PAD820,
      PAD810U == "W" ~ PAD810Q *PAD820 /7,
      PAD810U == "M" ~ PAD810Q *PAD820 /30,
      PAD810U == "Y" ~ PAD810Q *PAD820 /360,
      TRUE ~ 0
    )
  )

#head(interview_data)

  
#head(interview_data)

interview_data <- interview_data %>%
  mutate(
    drinking = case_when(
      ALQ111 == 1 ~ 1,
      ALQ111 == 2 ~ 0,
      ALQ111 == 9 | is.na(ALQ111) ~ 0
    )
  )
interview_data <- interview_data %>%
  mutate(ALQ121 = replace_na(ALQ121, 0))




interview_data <- interview_data %>%
  mutate(IND310 = case_when(
    IND310 %in% c(77, 99) ~ NA_real_,
    TRUE ~ IND310
  ))

#unique(interview_data$IND310)
interview_data <- interview_data %>% select(-"SMQ040", -"PAD790Q", -"PAD790U", -"PAD800", -"PAD810Q", -"PAD810U", -"PAD820")
#nrow(interview_data)
#nrow(interview_data %>% select(-IND310))

```
Random Forest
```{r}
weights <- weights(interview_design)
rf_data <- interview_data %>%
  select("RIAGENDR", "RIDRETH1", "RIDRETH3",  "DMDBORN4", "DMDEDUC2", "DMDMARTZ", "DMDHHSIZ", "PAD680", "ALQ111", "ALQ121", "IND310", "SLD012", "SLD013", "age", "smoking", "vigorous_time", "moderate_time",  "drinking", "diabetes", "prediabetes", "nondiabetes")
#head(rf_predictors)
# 
# 
# # set.seed(100)
# # rf_diabetes<-randomForest(as.factor(rf_data$diabetes)~.-prediabetes-nondiabetes,data=rf_data,mtry=12,ntree=1000,na.action = na.roughfix)
# # plot(rf_diabetes)
# # rf_diabetes<-randomForest(as.factor(rf_data$prediabetes)~.-diabetes-nondiabetes,data=rf_data,mtry=12,ntree=1000,na.action = na.roughfix)
# # plot(rf_prediabetes)  
# # rf_nondiabetes<-randomForest(as.factor(rf_data$nondiabetes)~.-prediabetes-diabetes,data=rf_data,mtry=12,ntree=1000,na.action = na.roughfix)
# # plot(rf_nondiabetes)  
# 

# rf_diabetes <- randomForest(
#   factor(diabetes) ~ . - prediabetes - nondiabetes,
#   data = rf_data,
#   ntree = 250,
#   weights = weights(interview_design),  # 使用survey weights
#   importance = TRUE,
#   na.action = na.roughfix
# )
# 
# rf_prediabetes <- randomForest(
#   factor(prediabetes) ~ . - diabetes - nondiabetes,
#   data = rf_data,
#   ntree = 250,
#   weights = weights(interview_design),
#   importance = TRUE,
#   na.action = na.roughfix
# )
# 
# rf_nondiabetes <- randomForest(
#   factor(nondiabetes) ~ . - diabetes - prediabetes,
#   data = rf_data,
#   ntree = 250,
#   weights = weights(interview_design),
#   importance = TRUE,
#   na.action = na.roughfix
# )
# 

# imp_diabetes <- importance(rf_diabetes)
# varImpPlot(rf_diabetes, main="Variable Importance for Diabetes")
# 
# imp_prediabetes <- importance(rf_prediabetes)
# varImpPlot(rf_prediabetes, main="Variable Importance for Prediabetes")
# 
# imp_nondiabetes <- importance(rf_nondiabetes)
# varImpPlot(rf_nondiabetes, main="Variable Importance for Non-diabetes")



pca_data<-rf_data %>% select(-"IND310")

```
PCA
```{r}
interview_data <- interview_data %>%
  mutate(DMDMARTZ = case_when(
    DMDMARTZ %in% c(77, 99) ~ 0,
    TRUE ~ DMDMARTZ
  ))
interview_data <- interview_data %>%
  mutate(DMDEDUC2 = case_when(
    DMDEDUC2 %in% c(9) ~ 0,
    TRUE ~ DMDEDUC2
  ))
library(PCAmixdata)
df <- as.data.frame(interview_data)
df[is.na(df)] <- 0
num_vars <- c("age", "vigorous_time", "moderate_time",  "DMDHHSIZ", "ALQ121",  "SLD012", "SLD013", "PAD680")
cat_vars <- c("RIAGENDR","RIDRETH1", "RIDRETH3", "DMDBORN4", "DMDEDUC2", "DMDMARTZ", "ALQ111", "diabetes", "prediabetes", "nondiabetes", "smoking", "drinking" )

X1 <- df[, num_vars]
X2 <- df[, cat_vars]
X2 <- data.frame(lapply(X2, as.factor))
#summary(X2)

library(PCAmixdata)
res.pcamix <- PCAmix(X.quanti = X1, X.quali = X2, 
                     graph = TRUE,
                     ndim = 5,
                     rename.level = TRUE)
print(res.pcamix$eig)

print(res.pcamix$sqload)

plot(res.pcamix$eig[,1], type="b", 
     xlab="Component number", 
     ylab="Eigenvalues",
     main="Scree Plot")




library(xtable)
sqload_df <- as.data.frame(res.pcamix$sqload)
latex_table <- xtable(sqload_df, digits = 4)
print(latex_table, type = "latex")

```
Age, SLD013(Sleep hours - weekends), Moderate (Excercise) Time, RIAGEND( Gender), DMDEDUC2( Education Level), ALQ121( How Often Drink Alcohol Bev), DMDMARTZ( Marital status)


Variable Selection
Examination Data
```{r}
exam_data<- data %>% select("WTSAF2YR",  "WTMEC2YR", "SDMVSTRA","SDMVPSU",  "BMXWT", "BMXRECUM", "BMXHEAD", "BMXHT", "BMXBMI", "BMXLEG", "BMXARML", "BMXARMC", "BMXWAIST", "BMXHIP", "diabetes", "prediabetes", "nondiabetes")
exam_data$diabetes_risk <- ifelse(exam_data$diabetes == 1 | exam_data$prediabetes == 1, 1, 0)
exam_design <- svydesign(
  id = ~SDMVPSU,
  strata = ~SDMVSTRA,
  weights = ~WTMEC2YR,
  data = exam_data,
  nest = TRUE
)
exam_data<- exam_data %>% select( "WTMEC2YR", "BMXWT", "BMXRECUM", "BMXHEAD", "BMXHT", "BMXBMI", "BMXLEG", "BMXARML", "BMXARMC", "BMXWAIST", "BMXHIP", "diabetes_risk")


exam_data<- exam_data %>% select(-"BMXRECUM", -"BMXHEAD")
exam_data<-na.omit(exam_data)
#nrow(exam_data)
```
Factor Analysis
```{r}
library(psych)
library(GPArotation)
vars_for_fa <- c("BMXWT", "BMXHT", "BMXLEG", "BMXARML", "BMXARMC", "BMXWAIST", "BMXHIP")
X <- exam_data[, vars_for_fa]


fa.parallel(X, fa="fa", n.iter=100, fm="ml")

fa_fit <- fa(X, 
            nfactors=3,
            rotate="varimax",
            fm="ml")
#>0.3
print(fa_fit, cut=.3)





library(xtable)
loadings <- fa_fit$loadings
loadings <- unclass(loadings)
loadings[abs(loadings) < 0.3] <- NA
loadings_df <- data.frame(unclass(loadings))
latex_table <- xtable(loadings_df, digit=2 ,cut=.3)
print(latex_table, type = "latex")

```




Data Processing
```{r}
data <- data %>%
  mutate(
    moderate_time = case_when(
      PAD790U == "D" ~ PAD790Q *PAD800,
      PAD790U == "W" ~ PAD790Q *PAD800 /7,
      PAD790U == "M" ~ PAD790Q *PAD800 /30,
      PAD790U == "Y" ~ PAD790Q *PAD800 /360,
      TRUE ~ 0
    )
  )

data <- data %>%
  mutate(DMDMARTZ = case_when(
    DMDMARTZ %in% c(77, 99) ~ 0,
    TRUE ~ DMDMARTZ
  ))


data <- data %>%
  mutate(
    drinking = case_when(
      ALQ111 == 1 ~ 1,
      ALQ111 == 2 ~ 0,
      ALQ111 == 9 | is.na(ALQ111) ~ 0
    )
  )

data <- data %>%
  mutate(
    ALQ121 = case_when(
      ALQ121 == 0 ~ 0,
      TRUE ~ 1))


data <- data %>%
  mutate(ALQ121 = replace_na(ALQ121, 0))

data$diabetes_risk <- ifelse(data$diabetes == 1 | data$prediabetes == 1, 1, 0)


design <- svydesign(
    id = ~SDMVPSU,
    strata = ~SDMVSTRA,
    weights = ~WTMEC2YR,
    data = data,
    nest = TRUE
)


processed_data<- data %>% select("diabetes_risk", "age", "RIAGENDR", "SLD013", "ALQ121", "DMDMARTZ", "BMXHT", "BMXWT", "BMXHIP", "moderate_time", "SDMVPSU", "SDMVSTRA","WTMEC2YR")
processed_data<-na.omit(processed_data)
#head(processed_data)

```




Data Processing and Train/ Test Set Split
```{r}
#split dataset
processed_data <- na.omit(processed_data)
#nrow(interview_data)
set.seed(1000)
train_index <- sample(1:nrow(processed_data), 0.8 * nrow(processed_data))



train_data <- processed_data[train_index, ]
test_data <- processed_data[-train_index, ]
train_weights <- weights[train_index]
test_weights <- weights[-train_index]



```



Model Construction
Logistics Regression
```{r}
#head(train_data)

lr_train_data <- train_data %>%
  mutate(BMXWT = BMXWT, BMXHT = BMXHT, BMXHIP = BMXHIP, age = age, SLD013 = SLD013, moderate_time = moderate_time, 
         ALQ121 = as.factor(ALQ121), RIAGENDR = as.factor(RIAGENDR), DMDMARTZ = as.factor(DMDMARTZ), SDMVPSU=SDMVPSU, 
         WTMEC2YR=WTMEC2YR, SDMVSTRA=SDMVSTRA)

lr_train_design <- svydesign(
  id = ~SDMVPSU,
  strata = ~SDMVSTRA,
  weights = ~WTMEC2YR,
  data = lr_train_data,
  nest = TRUE
)

model_logistic <- svyglm(diabetes_risk ~ BMXWT+ BMXHT+ BMXHIP+ age + SLD013+ moderate_time+  ALQ121 + RIAGENDR + DMDMARTZ  ,
                         data = lr_train_data,
                         design = lr_train_design,
                         family = quasibinomial())


#summary(model_logistic)

# model_summary <- summary(model_logistic)
# latex_table <- xtable(model_summary)
# print(latex_table, 
#       type = "latex")
# 

lr_test_data <- test_data %>%
  mutate(BMXWT = BMXWT, BMXHT = BMXHT, BMXHIP = BMXHIP, age = age, SLD013 = SLD013, moderate_time = moderate_time, 
         ALQ121 = as.factor(ALQ121), RIAGENDR = as.factor(RIAGENDR), DMDMARTZ = as.factor(DMDMARTZ), SDMVPSU=SDMVPSU, 
         WTMEC2YR=WTMEC2YR, SDMVSTRA=SDMVSTRA)


```


SVM
```{r}

svm_train_data <- train_data %>%
  mutate(BMXWT = scale(BMXWT), BMXHT = scale(BMXHT), BMXHIP = scale(BMXHIP), age = scale(age), SLD013 = scale(SLD013), moderate_time = scale(moderate_time), 
         ALQ121 = as.factor(ALQ121), RIAGENDR = as.factor(RIAGENDR), DMDMARTZ = as.factor(DMDMARTZ),
         SDMVPSU=SDMVPSU, WTMEC2YR=WTMEC2YR, SDMVSTRA=SDMVSTRA)


svm_model<-svm(diabetes_risk~.,data=svm_train_data,kernel="radial")

svm_test_data <- train_data %>%
  mutate(BMXWT = scale(BMXWT), BMXHT = scale(BMXHT), BMXHIP = scale(BMXHIP), age = scale(age), SLD013 = scale(SLD013), moderate_time = scale(moderate_time), 
         ALQ121 = as.factor(ALQ121), RIAGENDR = as.factor(RIAGENDR), DMDMARTZ = as.factor(DMDMARTZ),
         SDMVPSU=SDMVPSU, WTMEC2YR=WTMEC2YR, SDMVSTRA=SDMVSTRA)
svm_test_design <- svydesign(
  id = ~SDMVPSU,
  strata = ~SDMVSTRA,
  weights = ~WTMEC2YR,
  data = svm_test_data,
  nest = TRUE
)





```



XGBOOST
```{r}
xgb_train_data <- train_data %>%
  mutate(BMXWT = as.numeric(BMXWT), BMXHT = as.numeric(BMXHT), BMXHIP = as.numeric(BMXHIP), age = as.numeric(age), SLD013 = as.numeric(SLD013), moderate_time = as.numeric(moderate_time), 
         ALQ121 = as.numeric(as.factor(ALQ121)), RIAGENDR = as.numeric(as.factor(RIAGENDR)), DMDMARTZ = as.numeric(as.factor(DMDMARTZ)),
         SDMVPSU=SDMVPSU, WTMEC2YR=WTMEC2YR, SDMVSTRA=SDMVSTRA)




train_matrix <- as.matrix(xgb_train_data[, !(names(xgb_train_data) %in% c("diabetes_risk", "WTMEC2YR", "SDMVPSU", "SDMVSTRA"))])
train_label <- xgb_train_data$diabetes_risk
train_weight <- xgb_train_data$WTMEC2YR
train_weight <- train_weight / mean(train_weight) 

dtrain <- xgb.DMatrix(
  data = train_matrix, 
  label = train_label,
  weight = train_weight
)


params <- list(
  objective = "binary:logistic",
  eval_metric = "auc",
  max_depth = 3,
  eta = 0.1,
  subsample= 0.8,
  colsample_bytree=0.9,
  min_child_weight=1,
  gamma = 0.1
)



# xgb_model <- xgb.train(
#   params = params,
#   data = dtrain,
#   nrounds = 100,
#   watchlist = list(train = dtrain),
#   early_stopping_rounds = 10,
#   print_every_n = 10
# )










xgb_test_data <- test_data %>%
  mutate(BMXWT = as.numeric(BMXWT), BMXHT = as.numeric(BMXHT), BMXHIP = as.numeric(BMXHIP), age = as.numeric(age), SLD013 = as.numeric(SLD013), moderate_time = as.numeric(moderate_time), 
         ALQ121 = as.numeric(as.factor(ALQ121)), RIAGENDR = as.numeric(as.factor(RIAGENDR)), DMDMARTZ = as.numeric(as.factor(DMDMARTZ)),
         SDMVPSU=SDMVPSU, WTMEC2YR=WTMEC2YR, SDMVSTRA=SDMVSTRA)

test_matrix <- as.matrix(xgb_test_data[, !(names(xgb_test_data) %in% c("diabetes_risk", "WTMEC2YR", "SDMVPSU", "SDMVSTRA"))])
test_label <- xgb_test_data$diabetes_risk
test_weight <- xgb_test_data$WTMEC2YR
test_weight <- test_weight / mean(test_weight) 
dtest <- xgb.DMatrix(
  data = test_matrix, 
  label = test_label,
  weight = test_weight
)
xgb_model <- xgb.train(
  params = params,
  data = dtrain,
  nrounds = 100,
  watchlist = list(train = dtrain, test = dtest),
  early_stopping_rounds = 10
)


test_pred <- predict(xgb_model, dtest)



```




test ROC&AUC
```{r}
#LR
lr_pred_prob <- predict(model_logistic, lr_test_data,  type = "response")
lr_roc_obj <- roc(lr_test_data$diabetes_risk ~ lr_pred_prob)


par(pty="s") 

coords <- coords(lr_roc_obj, "all")
plot(1-coords$specificity, coords$sensitivity,
     type="l", 
     xlim=c(0,1), 
     ylim=c(0,1),
     col="red",
     lwd=2,
     main="ROC Curve",
     xlab="1-Specificity",
     ylab="Sensitivity")

abline(0, 1, col="gray", lty=2)

legend("bottomright",
       legend = c(paste("Testing (AUC =", round(auc(lr_roc_obj), 3), ")")),
       col = "red",
       lwd = 2)






















#SVM
svm_pred_prob <- predict(svm_model, svm_test_data,  type = "response")


svm_roc_obj <- roc(svm_test_data$diabetes_risk ~ svm_pred_prob)

coords <- coords(svm_roc_obj, "all")
plot(1-coords$specificity, coords$sensitivity,
     type="l", 
     xlim=c(0,1), 
     ylim=c(0,1),
     col="red",
     lwd=2,
     main="ROC Curve",
     xlab="1-Specificity",
     ylab="Sensitivity")

abline(0, 1, col="gray", lty=2)

legend("bottomright",
       legend = c(paste("Testing (AUC =", round(auc(svm_roc_obj), 3), ")")),
       col = "red",
       lwd = 2)



#xgb
test_roc <- roc(test_label, test_pred, weights = test_weight)

coords <- coords(test_roc, "all")
plot(1-coords$specificity, coords$sensitivity,
     type="l", 
     xlim=c(0,1), 
     ylim=c(0,1),
     col="red",
     lwd=2,
     main="ROC Curve",
     xlab="1-Specificity",
     ylab="Sensitivity")

abline(0, 1, col="gray", lty=2)

legend("bottomright",
       legend = c(paste("Testing (AUC =", round(auc(test_roc), 3), ")")),
       col = "red",
       lwd = 2)

```

```{r}
par(pty="s")

coords_lr <- coords(lr_roc_obj, "all")
plot(1-coords_lr$specificity, coords_lr$sensitivity,
     type="l", 
     xlim=c(0,1), 
     ylim=c(0,1),
     col="red",
     lwd=2,
     main="ROC Curves Comparison",
     xlab="1-Specificity",
     ylab="Sensitivity")

coords_svm <- coords(svm_roc_obj, "all")
lines(1-coords_svm$specificity, coords_svm$sensitivity,
      col="blue",
      lwd=2)

coords_xgb <- coords(test_roc, "all")
lines(1-coords_xgb$specificity, coords_xgb$sensitivity,
      col="green",
      lwd=2)

abline(0, 1, col="gray", lty=2)

legend("bottomright",
       legend = c(
           paste("LR (AUC =", round(auc(lr_roc_obj), 3), ")"),
           paste("SVM (AUC =", round(auc(svm_roc_obj), 3), ")"),
           paste("XGB (AUC =", round(auc(test_roc), 3), ")")
       ),
       col = c("red", "blue", "green"),
       lwd = 2)
```



